Mechanising a linear \picalc

### 2020-04-28 paper/paper.tex
Change the order of the theorems

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Subject Reduction}
\label{subject-reduction}

@@

When function abstraction and application come together in the \lambdacalc{} with de Bruijn indices, every reference to the innermost variable in the body of the abstraction gets replaced with the argument of the application.
In the \picalc{} however substitution takes another form: every reference to the innermost variable in the receiving process gets replaced with the reference to the data that is being sent over the channel.
In a resource-aware \picalc{}, that means that instead of exhausting all $m$ multiplicities of the innermost variable, we leave those unaltered and exhaust them from the element that is being sent.

\begin{nitheorem}
  \label{thm:substitution}
  Let $P$ be a process where the innermost variable has all its $m$ multiplities exhausted, such that $\types{\gamma , t}{\Gamma , m}{P}{\Psi , \ell_{\o}}$.
  Let $j$ be the index of the data that is being received.
  This data has at least $m$ multiplicities, such that $\contains{\gamma}{\Psi}{j}{t}{m}{\Xi}$.
  Then, we can substitute the innermost variable by $j$.
  As a result, we will exhaust no multiplicities on the innermost variable and exhaust them in $j$ instead, such that $\types{\gamma , t}{\Gamma , m}{\subst{P}{j}{\constr{zero}}}{\Xi , m}$.
\end{nitheorem}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Type Safety}
\label{type-safety}

\todo{intro}

@@

When function abstraction and application come together in the \lambdacalc{} with de Bruijn indices, every reference to the innermost variable in the body of the abstraction gets replaced with the argument of the application.
In the \picalc{} however substitution takes another form: every reference to the innermost variable in the receiving process gets replaced with the reference to the data that is being sent over the channel.
In a resource-aware \picalc{}, that means that instead of exhausting all $m$ multiplicities of the most recent variable, we leave those unaltered and exhaust them from the variable that is being received.

\begin{nitheorem}
  \label{thm:substitution}
  Let $P$ be a process where the innermost variable has all its $m$ multiplities exhausted, such that $\types{\gamma , t}{\Gamma , m}{P}{\Psi , \ell_{\o}}$.
  Let $j$ be the index of the data that is being received.
  This data has at least $m$ multiplicities, such that $\contains{\gamma}{\Psi}{j}{t}{m}{\Xi}$.
  Then, we can substitute the most recent variable by $j$.
  As a result, we will exhaust no multiplicities on the innermost variable and exhaust them in $j$ instead, therefore $\types{\gamma , t}{\Gamma , m}{\subst{P}{j}{\constr{zero}}}{\Xi , m}$.
\end{nitheorem}

@@

\subsection{Subject Reduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
